---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r Settings.Code.Chunk, include = FALSE, purl = FALSE}
knitr::opts_chunk$set(cache = FALSE, collapse = TRUE, comment = "#>", echo = TRUE, engine = "R", error = FALSE, eval = TRUE, fig.path = "man/figures/README-", fig.align = "center", fig.height = 5, fig.width = 7, out.width = "100%", highlight = TRUE, include = TRUE, message = TRUE, prompt = FALSE, purl = TRUE, results = "markup", rows.print = 5, strip.white = TRUE, tidy = FALSE, tidy.opts = list(width.cutoff = 80), warning = TRUE)
```

# okara
<!-- badges: start -->
`r badger::badge_license()`
`r badger::badge_devel("omerkara/okara", "blue")`
[![star this repo](https://githubbadges.com/star.svg?user=omerkara&repo=okara&style=default)](https://github.com/omerkara/okara)
[![fork this repo](https://githubbadges.com/fork.svg?user=omerkara&repo=okara&style=default)](https://github.com/omerkara/okara/fork)
<!-- badges: end -->

[Ömer Kara](https://drive.google.com/file/d/1riCNALzVc6QsYIGVIlfGYIeEqMLQ_jfQ/preview)

---

R/okara is an [R](https://www.r-project.org/) package with miscellaneous R functions that are useful to me. Additionally, some of these R functions are frequently used by students in [my courses](https://akademiekonometri.netlify.app/courses/).

---

## Installation
To install `okara` package, you need to install and/or load the [`devtools`](https://devtools.r-lib.org//index.html) package. The below code automatically installs and/or loads it for you.
``` {r devtools.package, message = FALSE, results = "hide"}
if("devtools" %in% rownames(utils::installed.packages()) == FALSE) {suppressWarnings(suppressMessages(install.packages("devtools")))}
suppressWarnings(suppressMessages(library("devtools")))
```

You can install the `okara` package from [GitHub](https://github.com/omerkara/okara) with the code below.
``` {r install.package.main, eval = FALSE, message = FALSE, results = "hide"}
devtools::install_github("omerkara/okara")
```

You can also use the below codes to install the `okara` package with dependencies and vignettes.
``` {r install.package.add, eval = FALSE}
devtools::install_github("omerkara/okara", dependencies = TRUE) ## With dependencies.
devtools::install_github("omerkara/okara", build_vignettes = TRUE) ## Builds the vignette on the fly.
```

## Loading
You can load the `okara` package with the code below.
``` {r install.package, include = FALSE, message = FALSE, results = "hide"}
if("okara" %in% rownames(utils::installed.packages()) == FALSE) {suppressWarnings(suppressMessages(devtools::install_github("omerkara/okara", force = FALSE)))}
```
``` {r load.package}
library("okara")
```

## Get Help
You can get help about the `okara` package with the code below.
``` {r help.package}
help(package = "okara")
```
